Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-15 paper/main.tex
Expanded chosen candidates section

Since Tahoe-\ac{LAFS} is using \ac{SHA}-256 internally, we only test \ac{SHA}-3
functions with 256-bit output in our implementation. The results of \ac{SHA}-3
256-bit functions and \ac{SHA}-256 benchmarking in \ac{SUPERCOP} can be seen in
tables \ref{tbl:supercop:long}, \ref{tbl:supercop:4096},
\ref{tbl:supercop:1536}, \ref{tbl:supercop:576}, \ref{tbl:supercop:64} and
\ref{tbl:supercop:8}. The lower the numbers, the faster the algorithms
performed in the test.

@@

We then chose the fastest implementation of each candidate that conforms to the
following criteria:
\begin{enumerate}
  \item The implementation must have an \ac{API} defined in C.
  \item The implementation must include a working \verb update() function.
  \item The implementation must not use assembly that can not be made
    position independent by \ac{GCC}.
  \item The implementation should conform to the \acp{KAT} specified in the
    \ac{NIST} submission package, or later updates by the author.
\end{enumerate}

>>>>

Since Tahoe-\ac{LAFS} is using \ac{SHA}-256 internally, we only test \ac{SHA}-3
functions with 256-bit output in our implementation.

\subsection{\ac{SUPERCOP} benchmarks}
The results of \ac{SHA}-3
256-bit functions and \ac{SHA}-256 benchmarking in \ac{SUPERCOP} can be seen in
tables \ref{tbl:supercop:long}, \ref{tbl:supercop:4096},
\ref{tbl:supercop:1536}, \ref{tbl:supercop:576}, \ref{tbl:supercop:64} and
\ref{tbl:supercop:8}. The lower the numbers, the faster the algorithms
performed in the test.

@@

\subsection{Criteria for implementation selection}

We chose the fastest implementation of each candidate that conforms to the
following criteria:
\begin{enumerate}
  \item The implementation must have an \ac{API} defined in C.
  \item The implementation must include a working \verb update() function.
  \item The implementation must not use assembly that can not be made
    position independent by \ac{GCC}.
  \item The implementation should conform to the \acp{KAT} specified in the
    \ac{NIST} submission package, or later updates by the author.
\end{enumerate}

% TODO fix kilde
Based on these criteria, we choose the fastest possible implementation based
on our benchmark in \ac{SUPERCOP}. The relative speed of each implementation, in
relation to other implementation for the same and other candidates are
available at source.

\subsection {Chosen implementations}

The chosen implementations are shown in \ref{tbl:sha3:implementations} and
their compiler flags used, which are extracted from the \ac{SUPERCOP} results
can be seen in \ref{tbl:sha3:compilerflags}. It should be noted that 32 in
blake32 does not refer to the output length of the function, but the fact that
the algorithm is optimized for 32-bit usage. 512 in Keccackc512 also does not
mean 512-bit output, but 512 cycles in the internal function. For the most part
we have found working versions of all candidates in \ac{SUPERCOP}, however
there are some exceptions.

\paragraph{JH} seems to be broken in every implementation with regard to
criteria 2. For both the optimized versions found in \ac{SUPERCOP} and the
reference implementations in the \ac{NIST} submission package, Hash("foofoo")
will not give the same result as two consecutive calls to Update("foo").
However the implementation in sphlib does fulfill this requirement. We have
also contacted the author, Thomas Pornin, which confirms this problem with the
official JH candidate and that the author has been made aware of the problem
but has not released any updated version yet.
% TODO: Fix hvordan vi referer til e-post?

\paragraph{Cubehash} sadly does not have a version in supercop with a 256-bit
ouput, which is why we have only included a version from sphlib.

\input{tables/sha3_implementations}
\input{tables/sha3_flags}
